### 2014-11-07 store-opsem.tex
Fixed typos

The state of an operational execution ($\E$) is a tuple $\Exec$ where
$\EffSoup$ is a set of effects, and $\visZ$, $\soZ$, $\sameobjZ$
$\subseteq$ $\EffSoup \times \EffSoup$ are \emph{visibility},
\emph{session order}, and \emph{same object} relations over effects,
respectively. We concretize an effect ($\eff$) as a tuple
$(s,i,op,v)$, which records the fact that $i^{th}$ action in session
with {\sf SessID} $s$, which is an operation $op$ on the replicated
object, has been successfully executed on some replica yielding a
return value $v$. Note that the combination of $s$ and $i$ uniquely
identifies the effect. Session order relation ($\soZ$) relates effects
generated by the same session.  An effect $\eff = (s,i,op,v)$ is said
to precede another effect $\eff' = (s',i',op',v')$ in session order if
and only if $s'=s$ and $i'\ge i$. Since we only consider one
replicated object in our formalization, the $\sameobjZ$ relation
relates every pair of effects in the effect soup ($\EffSoup$). An
effect generated at a replica becomes visible at rest of the replicas
eventually.  If we denote the effect generated by the operation $op$
as $\eff_{op}$, then $\Theta(r) \times \{\eff_{op}\} ~\subseteq~
\visZ$. Often, in our formalization, we use $\visZ$ and $\soZ$ binary
relations to obtain a set of effects visible to a given effect $\eff$,
or set of effects that precede a given effect $\eff$ in the session
order. As a syntactic convenience, whenever $R$ is a binary relation,
we write $R(\eff)$ to denote the set of all $\eff'$ such that
$(\eff,\eff') \in R$.  Conversely, we write $R^{-1}(\eff)$ to denote
the set of all $\eff'$ such that $(\eff',\eff) \in R$.

@@

\begin{theorem}[Soundness Modulo Classification]
\label{thm:weak-soundness}
For every well-formed execution state $\E$, and contract class $\tau 
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i,\sigma \rangle \Sigma')
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv_{\tau}[\eff/\cureff]$
\end{theorem}
\begin{proof}
  By case analysis on $(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
  \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
  \langle s,i,\sigma \rangle \Sigma')$. 
  \GK{Lets first finalize all notations, rules, and also agree on
  all theorem statements. This way we don't have to change the proof
  again.} 
\end{proof}

\begin{corollary}[Soundness]
\label{thm:soundness}
For every well-formed execution state $\E$, and contract class $\tau
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, and for every consistency
contract $\cv$ in the contract class $\tau$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i,\sigma \rangle \Sigma')
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv[\eff/\cureff]$
\end{corollary}
\begin{proof}
Follows from Theorems~\ref{thm:classification-sound} and
\ref{thm:weak-soundness}
\qed
\end{proof}

>>>>

The state of an operational execution ($\E$) is a tuple $\Exec$ where
$\EffSoup$ is a set of effects, and $\visZ$, $\soZ$, $\sameobjZ$
$\subseteq$ $\EffSoup \times \EffSoup$ are \emph{visibility},
\emph{session order}, and \emph{same object} relations over effects,
respectively. We define an effect ($\eff$) as a tuple
$(s,i,op,v)$, which records the fact that $i^{th}$ action in session
with {\sf SessID} $s$, which is an operation $op$ on the replicated
object, has been successfully executed on some replica yielding a
return value $v$. Note that the combination of $s$ and $i$ uniquely
identifies the effect. Session order relation ($\soZ$) relates effects
generated by the same session.  An effect $\eff = (s,i,op,v)$ is said
to precede another effect $\eff' = (s',i',op',v')$ in session order if
and only if $s'=s$ and $i'\ge i$. Since we only consider one
replicated object in our formalization, the $\sameobjZ$ relation
relates every pair of effects in the effect soup ($\EffSoup$). An
effect generated at a replica becomes visible at rest of the replicas
eventually.  If we denote the effect generated by the operation $op$
as $\eff_{op}$, then $\Theta(r) \times \{\eff_{op}\} ~\subseteq~
\visZ$. Often, in our formalization, we use $\visZ$ and $\soZ$ binary
relations to obtain a set of effects visible to a given effect $\eff$,
or set of effects that precede a given effect $\eff$ in the session
order. As a syntactic convenience, whenever $R$ is a binary relation,
we write $R(\eff)$ to denote the set of all $\eff'$ such that
$(\eff,\eff') \in R$.  Conversely, we write $R^{-1}(\eff)$ to denote
the set of all $\eff'$ such that $(\eff',\eff) \in R$.

@@

\begin{theorem}[Soundness Modulo Classification]
\label{thm:weak-soundness}
For every well-formed execution state $\E$, and contract class $\tau 
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i,\sigma \rangle \pll \Sigma')
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv_{\tau}[\eff/\cureff]$
\end{theorem}
\begin{proof}
  By case analysis on $(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
  \sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
  \langle s,i,\sigma \rangle \pll \Sigma')$. 
  \GK{Lets first finalize all notations, rules, and also agree on
  all theorem statements. This way we don't have to change the proof
  again.} 
\end{proof}

\begin{corollary}[Soundness]
\label{thm:soundness}
For every well-formed execution state $\E$, and contract class $\tau
\in \{{\sf ec},{\sf cc},{\sf sc}\}$, and for every consistency
contract $\cv$ in the contract class $\tau$, If:
\begin{smathpar}
(\E, \Theta, \langle s,i,\langle op,\tau \rangle;
\sigma \rangle \pll \Sigma) \xrightarrow{\eff} (\E', \Theta',
\langle s,i,\sigma \rangle \pll \Sigma')
\end{smathpar}
then (\romannumeral 1) $\E'$ is well-formed, and (\romannumeral 2)
$\E' \models \cv[\eff/\cureff]$
\end{corollary}
\begin{proof}
Follows from Theorems~\ref{thm:classification-sound} and
\ref{thm:weak-soundness}
\qed
\end{proof}
